% -- Encoding UTF-8 without BOM
% -- XeLaTeX => PDF (BIBER)

\documentclass[]{cv-style}          % Add 'print' as an option into the square bracket to remove colours from this template for printing. 
                                    % Add 'espanol' as an option into the square bracket to change the date format of the Last Updated Text
                                   

\sethyphenation[variant=british]{english}{} % Add words between the {} to avoid them to be cut 
\usepackage{fontawesome}

\begin{document}

\header{Shantanu}{ Deshpande}           % Your name

\lastupdated

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION  -- In the aside, each new line forces a line break
%----------------------------------------------------------------------------------------

\begin{aside}
%
\section{contact}\small
E-10, Ishwar Nagar
Bhandup, Mumbai-400078
India
~
+91 8275147406
~
shantanud106@gmail.com
~
%
\section{links}
Github ID:
\faGithub { iamShantanu101}
~
LinkedIn:
\faLinkedin { shantanud10}
~
%
\section{languages}
English fluency
%
\section{programming}
Python, Shell Scripting,
Java, C, HTML5
\LaTeX{}
%
\section{operating systems}
Linux, Unix, MacOS
%
\section{DevOps Tools}
Docker, Docker Swarm,
AWS, Git, Packer 
%
\end{aside}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{experience}

\begin{entrylist}
%------------------------------------------------
\entry
  {2015--Now}
  {C-Edge Technologies Pvt Ltd}
  {Mumbai, IN}
  {\jobtitle{Assistant Systems Analyst}\\
  Worked for Tata Consultancy Services Ltd banking sector clients. 
  \begin{itemize}
  \item Development in Banking Platform using prescribed guidelines in \\
        banking domain. 
  \item Automated redundant daily tasks in a unix environment using shell scripting.
  \end{itemize}
  }
%------------------------------------------------

\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{education}

\begin{entrylist}
%------------------------------------------------

\entry
{2008--2009}
{Secondary School(SSC) {\normalfont Lions Dnyanpeeth, Khamgaon [82.92]}}
{Maharashtra State Board}
{\vspace{-0.3cm}}
%------------------------------------------------
\entry
{2009--2011}
{Higher Secondary Education {\normalfont G.S. College, Khamgaon [61.82]}}
{Maharashtra State Board}
{\vspace{-0.3cm}}
%-------------------------------------------------
\entry
{2011--2015}
{B.Eng. {\normalfont in Computer Science and Engineering [68]}}
{Amravati University}
{ }
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	B.E. Coursework
%----------------------------------------------------------------------------------------

\section{graduate coursework}

\begin{entrylist}
%------------------------------------------------
\entry
{2015}
{Strategic Online Advertising} 
{STC, School of Engg, Shegaon}
{ Providing a Statistical Analysis on Online Advertising Algorithms. \\
  \textbf{Tools and Technolgies:} 1, Core Java 2, Oracle 11g}

%------------------------------------------------
\entry
{2013}
{Data Encryption in Cloud Computing using RSA Algorithm}
{International Conference}
{\textbf{Research Paper:} Survey of using RSA cryptographic algorithm for better cloud \\ security.}
{\vspace{-0.3cm}}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	ADDITIONAL PROJECTS
%----------------------------------------------------------------------------------------

\section{additional projects}

\begin{entrylist}
%------------------------------------------------
\entry
{2016}
{Twitter Sentiment Analysis using Machine Learning}
{ }
{Analysed the sentiments of tweets using various Machine Learning Techniques.
Used Maximum Entropy and Naive Bayes algorithms. Showing statistical graphs of sentiments of masses towards a specific topic.}

%------------------------------------------------
\entry
{2016}
{(Yet Another) Twitter Sentiment Analyzer using Apache Spark MLLIB}
{ }
{Analyzing the sentiments of twitterati’s in real time using Spark Streaming and MLLIB Used d3.js for visualisation purposes. Used naive bayes classifier. Docker images available. }

%------------------------------------------------
\entry
{2017}
{Weatherbot}
{ }
{Developed a FB Messenger Bot which gives weather on querying the Location name. Used openweathermap API for fetching weather details.}

{\hspace{-0.3cm}}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	AWARDS SECTION
%----------------------------------------------------------------------------------------

\section{awards}

\begin{entrylist}
%------------------------------------------------
\entry
{2015}
{Ethical Hacker Guru}
{STC, School of Engg, Shegaon}
{Took "HackZeal", a two day ethical hacking workshop.}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\section{interests}
  \vspace{-0.2cm}

\textbf{professional:} professional interest 1, open source technologies 2, automation and 3 ML/DL/AI 
%----------------------------------------------------------------------------------------

\end{document}